---
title: "Lab 09"
author: "Yuhong Hu"
date: "`r Sys.Date()`"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Set up
```{r}
library(RSQLite)
library(DBI)

# Initialize a temporary in memory database
con <- dbConnect(SQLite(), ":memory:")

# Download tables
actor <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/actor.csv")
rental <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/rental.csv")
customer <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/customer.csv")
payment <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/payment_p2007_01.csv")

# Copy data.frames to database
dbWriteTable(con, "actor", actor)
dbWriteTable(con, "rental", rental)
dbWriteTable(con, "customer", customer)
dbWriteTable(con, "payment", payment)
```

```{sql,connection=con}
PRAGMA table_info(actor)
```

An alterenatives would be
```{r}
dbGetQuery(con,
'PRAGMA table_info(actor)')
```

# Exercise 1
Retrive the actor ID, first name and last name for all actors using the actor table. Sort by last name and then by first name.

```{r}
dbGetQuery(con,
  "SELECT actor_id, first_name, last_name
  FROM actor 
  ORDER BY last_name, first_name
  ")
```
Try in SQL directly

```{sql,connection=con}
SELECT actor_id, first_name, last_name
FROM actor 
ORDER BY last_name, first_name
```


#Exercise 2

Retrive the actor ID, first name, and last name for actors whose last name equals ‘WILLIAMS’ or ‘DAVIS’.

```{r}

```

#Exercise 3

Write a query against the rental table that returns the IDs of the customers who rented a film on July 5, 2005 (use the rental.rental_date column, and you can use the date() function to ignore the time component). Include a single row for each distinct customer ID.

```{r}

```

# Exercise 4

```{r}

```

# clean up
```{r}
dbDisconnect(con)
```




