---
title: "lab04"
author: "Yuhong Hu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read in data
```{r}
if (!file.exists("met_all.gz"))
  download.file(
    url = "https://raw.githubusercontent.com/USCbiostats/data-science-data/master/02_met/met_all.gz",
    destfile = "met_all.gz",
    method   = "libcurl",
    timeout  = 60
    )
met <- data.table::fread("met_all.gz")
```
# Prepare the data
Remove temperatures less than -17C
Make sure there are no missing data in the key variables coded as 9999, 999, etc
Generate a date variable using the functions as.Date() (hint: You will need the following to create a date paste(year, month, day, sep = "-")).
Using the data.table::week function, keep the observations of the first week of the month.
Compute the mean by station of the variables temp, rh, wind.sp, vis.dist, dew.point, lat, lon, and elev.
Create a region variable for NW, SW, NE, SE based on lon = -98.00 and lat = 39.71 degrees
Create a categorical variable for elevation as in the lecture slides
```{r}

```

