---
title: "Lab 04"
author: "Yuhong Hu"
date: "`r Sys.Date()`"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(data.table)
library(lubridate)
library(cowplot)
```


# Read in data
```{r read-data,cache=TRUE}
if (!file.exists("/Users/rain/Desktop/PhD course/pm 566/pm566-fall2022-labs/lab04/met_all.gz"))
  download.file(
    url = "https://raw.githubusercontent.com/USCbiostats/data-science-data/master/02_met/met_all.gz",
    destfile = "met_all.gz",
    method   = "libcurl",
    timeout  = 60
    )
met <- data.table::fread("/Users/rain/Desktop/PhD course/pm 566/pm566-fall2022-labs/lab04/met_all.gz")
```
# Prepare the data
Remove temperatures less than -17C and change elev 9999 to NA

```{r remove_low_twmp}
met <- met[temp > -17][elev == 9999.0,elev := NA]
```


```{r create-ymd,cache=TRUE}
# Generate a date variable using the functions as.Date() (hint: You will need the following to create a date paste(year, month, day, sep = "-")).
met <- met[,ymd:=as.Date(paste(year,month,day,sep = "-"))]
```


```{r}
# Using the data.table::week function, keep the observations of the first week of the month.
met[,table(week(ymd))]
met <- met[week(ymd)==31]

# Compute the mean by station of the variables temp, rh, wind.sp, vis.dist, dew.point, lat, lon, and elev.
met_avg <- met[,.(
  temp = mean(temp,na.rm=TRUE),
  rh = mean(rh,na.rm=TRUE),
  wind.sp = mean(wind.sp,na.rm=TRUE),
  vis.dist = mean(vis.dist,na.rm=TRUE),
  dew.point = mean(dew.point,na.rm=TRUE),
  lat = mean(lat,na.rm=TRUE),
  lon = mean(lon,na.rm=TRUE),
  elev = mean(elev,na.rm=TRUE)
),by = 'USAFID']

# Create a region variable for NW, SW, NE, SE based on lon = -98.00 and lat = 39.71 degrees
met_avg[,region := fifelse(lon >= -98 & lat > 39.71,"NE",
              fifelse(lon < -98 & lat > 39.71,"NW",
              fifelse(lon < -98 & lat <= 39.71,"SW","SE")))]

table(met_avg$region)

# Create a categorical variable for elevation as in the lecture slides
met_avg[,elev_cat := fifelse(elev>252,'high','low')]
```

# geom_violin
Use geom_violin to examine the wind speed and dew point temperature by region.
```{r violin-dewpoint}
met_avg[!is.na(region)] %>% 
  ggplot()+
  geom_violin(mapping=aes(y=dew.point, x=1, color=region,fill=region))+
  facet_wrap(~region,nrow=1)
```
The highest dewpoint was reported in SE.

```{r violin-wind.sp}
met_avg[!is.na(region)&!is.na(wind.sp)] %>% 
  ggplot()+
  geom_violin(mapping=aes(y=wind.sp, x=1, color=region,fill=region))+
  facet_wrap(~region,nrow=2,ncol=2)
```

# gemo_jitter
Use geom_jitter with geom_smooth to examine the association between dew point temperature and wind speed by region
```{r scatterplot-dewpoint-wind.sp}
met_avg[!is.na(region)&!is.na(wind.sp)] %>% 
  ggplot(mapping=aes(y=dew.point,x=wind.sp))+
  geom_jitter(mapping=aes(color=region))+
  geom_smooth(method=lm,mapping=aes(linetype=region))+
  facet_wrap(~region,nrow=2)
```
#geom_bar
Use geom_bar to create barplots of the weather stations by elevation category coloured by region
```{r}

```

