---
title: "Lab 09"
author: "Yuhong Hu"
date: "`r Sys.Date()`"
output: 
       pdf_document: default
       word_document: default
       html_document: default
       github_document:
         html_preview: false
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(ggplot2)
# tinytex::install_tinytex()
```


# Problem 2: Before you
1. The following functions can be written to be more efficient without using parallel:

This function generates a `n x k` dataset with all its entries distributed poission with mean `lambda`
```{r}
set.seed(1235)
fun1 <- function(n = 100, k = 4, lambda = 4) {
  x <- NULL
  
  for (i in 1:n)
    x <- rbind(x, rpois(k, lambda))
  
  return(x)
}
f1<-fun1()
mean(f1)

fun1alt <- function(n = 100, k = 4, lambda = 4) {
  x<-matrix(rpois(n*k, lambda),ncol=4)
}

# Benchmarking
microbenchmark::microbenchmark(
  fun1(),
  fun1alt()
)
```

something about matrix
```{r}
d <- matrix(1:16, ncol=4)
d[2,1]
d[2]
diag(d)
d[c(1,6,11,16)]
cbind(1:4,1:4)
d[cbind(1:4,1:4)]
```

2. Find the column max (hint: Checkout the function `max.col()`).

```{r}
# Data Generating Process (10 x 10,000 matrix)
set.seed(1234)
M <- matrix(runif(12),ncol=4)
M

x <- matrix(rnorm(1e4), nrow=10)

# Find each column's max value
fun2 <- function(x) {
  apply(x, 2, max)
}

fun2(M)

fun2alt <- function(x) {
  idx <- max.col(t(x))
  x[cbind(idx,1:4)]
}

fun2alt(M)

# Benchmarking
microbenchmark::microbenchmark(
  fun2(x),
  fun2alt(x)
)
```


# Problem 3: Parallelize everything

We will now turn our attention to non-parametric bootstrapping. Among its many uses, non-parametric bootstrapping allow us to obtain confidence intervals for parameter estimates without relying on parametric assumptions.

The main assumption is that we can approximate many experiments by resampling observations from our original dataset, which reflects the population.

This function implements the non-parametric bootstrap:

```{r}
my_boot <- function(dat, stat, R, ncpus = 1L) {
  
  # Getting the random indices
  n <- nrow(dat)
  idx <- matrix(sample.int(n, n*R, TRUE), nrow=n, ncol=R)
 
  # Making the cluster using `ncpus`
  # STEP 1: GOES HERE
  # STEP 2: GOES HERE
  
    # STEP 3: THIS FUNCTION NEEDS TO BE REPLACES WITH parLapply
  ans <- lapply(seq_len(R), function(i) {
    stat(dat[idx[,i], , drop=FALSE])
  })
  
  # Coercing the list into a matrix
  ans <- do.call(rbind, ans)
  
  # STEP 4: GOES HERE
  
  ans
  
}
```



