---
title: "Lab 03"
author: "Yuhong Hu"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)
library(lubridate)
```



## Step1. Read in the data
First download and then read in with data.table:fread()
```{r}
if(!file.exists('met_all.gz')){
download.file("https://raw.githubusercontent.com/USCbiostats/data-science-data/master/02_met/met_all.gz", "met_all.gz", method="libcurl", timeout = 60)
}

met <- data.table::fread("met_all.gz")
```

## Step2. Check the dimensions, headers, footers. 
2377343 rows and 30 columns.
```{r}
dim (met)
head(met)
tail(met)

```

## Step3. Take a look at the variables.
```{r}
str(met)
```

## Step4. Take a closer look at the key variables.
```{r}
table(met$year)
table(met$day)
table(met$hour)
summary(met$temp)
summary(met$elev)
summary(met$wind.sp)
```


It looks like the elevation variable has observations with 9999.0, which is probably an indicator for missing. We should take a deeper look at the data dictionary to confirm. The wind speed variable is ok but there are a lot of missing data. After checking the data we should make the appropriate modifications. Replace elevations with 9999 as NA.

```{r}
met[met$elev==9999.0] <- NA
summary(met$elev)
```

The weather station with the highest elevation is at `r max(met$elev,na.rm=TRUE)` meters.

We also have the issue of the minimum temperature being -40C, so we should remove those observations.

```{r}
met <- met[temp>-40]
met2 <- met[order(temp)]
head(met2)
```
## Step5.Check the data against an external data source.
```{r}
met <- met[temp>-15]
met2 <- met[order(temp)]
head(met2)
```

## Step6. Calculate summary statistics
select the weather station with maximum elevation; look at the correlation between temperature and wind speed; look at the correlation between temperature and wind speed with hour and day of the month。
```{r}
elev <- met[elev==max(elev)]
summary(elev)

met[elev==max(elev,na.rm=TRUE),summary(temp)]
met[elev==max(elev,na.rm=TRUE),summary(wind.sp)]

met[elev==max(elev,na.rm=TRUE),.(temp_wind=cor(temp,wind.sp, use="complete"),
                                 temp_hour=cor(temp,hour, use="complete"),
                                 wind.sp_day = cor(wind.sp,day, use="complete"),
                                 wind.sp_hour = cor(wind.sp,hour, use="complete")
                                 )]
```

or alternatives.
```{r}
cor(elev$temp, elev$wind.sp, use="complete")

cor(elev$temp, elev$hour, use="complete")

cor(elev$wind.sp, elev$day, use="complete")

cor(elev$wind.sp, elev$hour, use="complete")

cor(elev$temp, elev$day, use="complete")


```

## Step7. Exploratory graphs
```{r}
hist(met$elev, breaks=100)

hist(met$temp)

hist(met$wind.sp)
```

Look at where the weather station with highest elevation is located.
```{r}
leaflet(elev) %>%
  addProviderTiles('OpenStreetMap') %>% 
  addCircles(lat=~lat,lng=~lon, opacity=1, fillOpacity=1, radius=100)
```

Look at the time series of temperature and wind speed at this location. For this we will need to create a date-time variable for the x-axis.
```{r}
elev$date <- with(elev, ymd_h(paste(year, month, day, hour, sep= ' ')))


summary(elev$date)

elev <- elev[order(date)]
head(elev)

plot(elev$date, elev$temp, type='l')

plot(elev$date, elev$wind.sp, type='l')
```

