---
title: "Lab 06"
author: "Yuhong Hu"
date: "`r Sys.Date()`"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
library(tidytext)
library(ggplot2)
library(forcats)
```


# Read in data
```{r read-data,cache=TRUE}
if (!file.exists("mtsamples.csv")){
  download.file(
    url = "https://raw.githubusercontent.com/USCbiostats/data-science-data/master/00_mtsamples/mtsamples.csv",
    destfile = "mtsamples.csv",
    method   = "libcurl",
    timeout  = 60
  )}

mts <- read.csv("mtsamples.csv")
str(mts)

mts <- as_tibble(mts)
```

# Question 1: What specialties do we have?
We can use count() from dplyr to figure out how many different catagories do we have? Are these catagories related? overlapping? evenly distributed?
```{r}
special <- mts %>%
  count(medical_specialty)

special %>%
  arrange(desc(n)) %>%
  knitr::kable()

length(unique(mts$medical_specialty))
```
There are `r nrow(special)` medical specialties.

```{r}
special %>%
  top_n(10,n)%>%
  ggplot(aes(x=n,y=fct_reorder(medical_specialty,n)))+
  geom_col()
```


# Question 2
Tokenize the the words in the transcription column.

- Count the number of times each token appears
- Visualize the top 20 most frequent words
- Explain what we see from this result. Does it makes sense? What insights (if any) do we get?
```{r cache=TRUE}
mts %>%
  unnest_tokens(token, transcription) %>%
  count(token,sort = TRUE)

## visualization
mts %>%
  unnest_tokens(word, transcription) %>%
  count(word) %>%
  top_n(20,n) %>%
  ggplot(aes(x=n,y=fct_reorder(word,n)))+
  geom_col()
  
```
A lots f stopwords here, no specific medical text.

# Question 3
- Redo visualization but remove stopwords before.
- Bonus points if you remove numbers as well.
- What do we see know that we have removed stop words? Does it give us a better idea of what the text is about?
```{r cache=TRUE}
mts %>%
  unnest_tokens(word, transcription) %>%
  anti_join(stop_words, by = "word") %>%
  count(word) %>%
  top_n(20,n) %>%
  ggplot(aes(x=n,y=fct_reorder(word,n)))+
  geom_col()
```
```{r}
mts %>%
  unnest_tokens(word, transcription) %>%
  anti_join(stop_words, by = "word") %>%
  # use regular expression to filter out numbers
  filter(!grepl(pattern = '^[0-9]+$',x=word))%>%
  count(word) %>%
  top_n(20,n) %>%
  ggplot(aes(x=n,y=fct_reorder(word,n)))+
  geom_col()
```


# Question 4
repeat question 2, but this time tokenize into bi-grams. how does the result change if you look at tri-grams?
```{r}
# Bigrams
mts %>%
  unnest_ngrams(bigram, transcription, n = 2) %>%
  count(bigram) %>%
  top_n(20,n) %>%
  ggplot(aes(x=n,y=fct_reorder(bigram,n)))+
  geom_col()
```
```{r}
# Trigrams
mts %>%
  unnest_ngrams(trigram, transcription, n = 3) %>%
  count(trigram) %>%
  top_n(20,n) %>%
  ggplot(aes(x=n,y=fct_reorder(trigram,n)))+
  geom_col()
```
Top 30 trigrams seemed to return a few more medical word group than bigrams.

# Question 5
Using the results you got from questions 4. Pick a word and count the words that appears after and before it.
```{r cache=TRUE}
ptbigram <- mts %>%
  unnest_ngrams(bigram, transcription, n = 2) %>%
  separate(bigram, into = c("word1", "word2"), sep = " ") %>%
  select(word1, word2) %>%
  filter(word1=='patient'|word2=='patient')
```

Words appearing before patients:
```{r cache=TRUE}
ptbigram %>%
  filter(word2=='patient') %>%
  count(word1, sort = TRUE) %>%
  anti_join(stop_words,by=c('word1'='word'))%>%
  top_n(10) %>%
  knitr::kable()
```
Words after
```{r cache=TRUE}
ptbigram %>%
  filter(word1=='patient') %>%
  count(word2, sort = TRUE) %>%
  anti_join(stop_words,by=c('word2'='word'))%>%
  top_n(10)%>%
  knitr::kable()
```


# Question 6
Which words are most used in each of the specialties. you can use group_by() and top_n() from dplyr to have the calculations be done within each specialty. Remember to remove stopwords. How about the most 5 used words?
```{r}
mts %>%
  unnest_tokens(word, transcription) %>%
  group_by(medical_specialty)%>%
  count(word,sort=TRUE) %>%
  # use regular expression to filter out numbers
  filter(!(word %in% stop_words$word) & !grepl(pattern = '^[0-9]+$',x=word))%>%
  top_n(5,n) %>%
  arrange(medical_specialty,desc(n)) %>%
  knitr::kable()
```








